Demographic Factors and Climate Action: Understanding How Age and Education Shape Sustainable Choices\thanks{Code and data are available at: \url{https://github.com/LexiKnight/toronto_climate/tree/main}.}

### 2024-12-14 paper/climate_change.qmd
last pushing attempt to render

## Software and R-packages
This project was conducted using the statistical software `R` [@citeR], with several packages facilitating data cleaning, analysis and reporting. The `tidyverse` package [@tidyverse] was central to the project, with `dplyr` [@dplyr] used in the cleaning and exploratory data analysis scripts for filtering, summarizing, and joining datasets. `readr` [@readr] handled reading and writing text data, while `tidyr` [@tidyr] reshaped data. `stringr` [@stringr] managed character strings, and `forecats` [@forecats] reordered factor levels for visualizations.

@@

# Results

## Model Summary Table
@fig-nineteen presents the accuracy of models predicting climate-friendly actions based on age and education. A threshold emerges from the data: models with accuracy above 50% are considered reliable, while those below require careful interpretation. Sorting waste correctly, with an accuracy of 59%, is the most reliable prediction, indicating a stronger association between demographic factors and this behavior. Models like home improvements (33%) offer limited predictive value but remain somewhat informative. In contrast, actions such as adopting meat alternatives (25%) or choosing electric or hybrid vehicles (25%) approach random chance, making their predictions less reliable for drawing meaningful conclusions.
```{r}
#| warning: false
#| echo: false
#| message: false
#| label: fig-nineteen
#| fig-cap: This table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on age and education. The accuracy values reflect how closely the model predictions align with the actual observed data. Higher accuracy values indicate better model performance.

@@

# Discussion

>>>>

## Software and R-packages
This project was conducted using the statistical software `R` [@citeR], with several packages facilitating data cleaning, analysis and reporting. The `tidyverse` package [@tidyverse] was central to the project, with `dplyr` [@dplyr] used in the cleaning and exploratory data analysis scripts for filtering, summarizing, and joining datasets. `readr` [@readr] handled reading and writing text data, while `tidyr` [@tidyr] reshaped data. `stringr` [@stringr] managed character strings, and `forcats` [@forcats] reordered factor levels for visualizations.

@@

# Results {#sec-results}

## Model Summary Table
@fig-nineteen presents the accuracy of models predicting climate-friendly actions based on age and education. A threshold emerges from the data: models with accuracy above 50% are considered reliable, while those below require careful interpretation. Sorting waste correctly, with an accuracy of 59%, is the most reliable prediction, indicating a stronger association between demographic factors and this behavior. Models like home improvements (33%) offer limited predictive value but remain somewhat informative. In contrast, actions such as adopting meat alternatives (25%) or choosing electric or hybrid vehicles (25%) approach random chance, making their predictions less reliable for drawing meaningful conclusions.

```{r}
#| warning: false
#| echo: false
#| message: false
#| results: hide
#| fig-cap: This table presents the accuracy of models predicting the likelihood of various climate-friendly actions based on age and education. See Table @fig-nineteen for details."
#| fig-names: model_accuracies

@@

# Discussion {#sec-discussion}

### 2024-12-14 paper/climate_change.tex
last pushing attempt to render

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}
\subsection{Introduction}\label{introduction}

@@

\subsection{Data}\label{sec-data}

@@

\subsubsection{Software and R-packages}\label{software-and-r-packages}

@@

\subsubsection{Methodology}\label{methodology}

\paragraph{Data Collection}\label{data-collection}

@@

\paragraph{Data Analysis}\label{data-analysis}

@@

\subsubsection{Features}\label{features}

\paragraph{Age}\label{age}

\subparagraph{Individual 2018}\label{individual-2018}

@@

\subparagraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021}

@@

\paragraph{Education}\label{education}

\subparagraph{Individual 2018}\label{individual-2018-1}

@@

\subparagraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-1}

@@

\paragraph{Extent Feel Informed}\label{extent-feel-informed}

\subparagraph{Individual 2018}\label{individual-2018-2}

@@

\subparagraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-2}

@@

\paragraph{Best Method of Delivery}\label{best-method-of-delivery}

\subparagraph{Individual 2018}\label{individual-2018-3}

@@

\subparagraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-3}

@@

\paragraph{Likelihood Taking Action}\label{likelihood-taking-action}

@@

\subsection{Model}\label{sec-model}

@@

\subsection{Results}\label{sec-results}

@@

\subsection{Discussion}\label{sec-discussion}

@@

\subsection{Appendix}\label{sec-appendix}

>>>>

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}
\section{Introduction}\label{introduction}

@@

\section{Data}\label{sec-data}

@@

\subsection{Software and R-packages}\label{software-and-r-packages}

@@

\subsection{Methodology}\label{methodology}

\subsubsection{Data Collection}\label{data-collection}

@@

\subsubsection{Data Analysis}\label{data-analysis}

@@

\subsection{Features}\label{features}

\subsubsection{Age}\label{age}

\paragraph{Individual 2018}\label{individual-2018}

@@

\paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021}

@@

\subsubsection{Education}\label{education}

\paragraph{Individual 2018}\label{individual-2018-1}

@@

\paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-1}

@@

\subsubsection{Extent Feel Informed}\label{extent-feel-informed}

\paragraph{Individual 2018}\label{individual-2018-2}

@@

\paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-2}

@@

\subsubsection{Best Method of Delivery}\label{best-method-of-delivery}

\paragraph{Individual 2018}\label{individual-2018-3}

@@

\paragraph{Comparison 2018 to 2021}\label{comparison-2018-to-2021-3}

@@

\subsubsection{Likelihood Taking Action}\label{likelihood-taking-action}

@@

\section{Model}\label{sec-model}

@@

\section{Results}\label{sec-results}

@@

\section{Discussion}\label{sec-discussion}

@@

\section{Appendix}\label{sec-appendix}
